Event Tracking Across Languages - Cross-Lngual Document Similarity and Event Tracking \todo{Better title...}

### 2015-03-20 rupnik2015.tex
minor
small change
Adds some material. Rough working outline of assigned work to Andrej.

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts}

@@

\subsection{Datasets}

@@

\subsection{Experiments With Missing Alignment Data}

{\oldText{Taken from XLite paper}
To investigate the empirical performance of our algorithm we will test it on a large-scale, real-world multilingual dataset that we extracted from Wikipedia  by  using so called 'inter-language' links as an alignment. We select a subset of Wikipedia languages containing three major languages, English--\emph{en} (hub language), Spanish--\emph{es}, Russian--\emph{ru}, and five minority (in the sense of Wikipedia sizes) languages, Slovenian--\emph{sl}, Piedmontese--\emph{pms}, Waray-Waray--\emph{war} (all with about 2 million native speakers), Creole--\emph{ht} (8 million native speakers), and Hindi--\emph{hi} (180 million native speakers). For preprocessing we remove the documents that contain less than 20 different words (stubs) and remove words occur in less than 50 documents as well as the top 100 most frequent words (in each language separately). We represent the documents as normalized TFIDF\cite{Salton88term-weightingapproaches} weighted vectors. These are languages with Wikipedia article sizes comparable to the minority languages.  (since the number of speakers does not directly correlate with the number of Wikipedia articles). The prime hub candidate is the English language which is well aligned with all other Wikipedia languages, although the alignment quality varies quite a bit. Furthermore, we remove the documents that contain less than 20 different words and remove words that are too infrequent as well as the top 100 most frequent words in the vocabularies. Furthermore, we call the document consisting of less than 20 different words, a stub. This documents are typically garbage, the titles of the columns in the table, remains of the parsing process, or Wikipedia articles with very little or no information contained in one or two sentences.

@@

In Section~\ref{sec:algorithms} we have described three main algorithms for identifying similar articles in different languages. These algorithms were $k$-means, LSI and CCA. To test which of these algorithms performs best we performed the following test. Using each algorithm, we analyzed all articles in Event Registry to find the most similar articles in other languages. The values of the cross-lingual article linking features (\texttt{linkCount} and \texttt{avgSimScore}) were then recomputed for all annotated learning examples. A dataset with only these two features and the label was constructed and used to test how accurate prediction models can be induced using the data. The results of the experiment are shown in Table~\ref{table:linkingEvalAlgos}. The table shows for each of the algorithms the obtained classification accuracy, precision and recall. We can see that the most informative features for cluster linking are obtained using the CCA algorithm, while $k$-means performs the worse. {\oldText{TODO:} add some explanation why this might be so.}

@@

\subsection{Scaling}

100 languages!
Describe the newsfeed volume, number of events and the number of similarities that need to be computed. Compare the memory requirements of our current implementation to the rest.
Comment on the caching gains in our implementation.

>>>>

\documentclass[twoside,11pt]{article}
\usepackage{jair, theapa, rawfonts}
\usepackage{graphicx}

@@

\subsection{Datasets}
\emph{Andrej started shuffling it, will do it till Monday :) }

@@

\subsection{Experiments With Missing Alignment Data}
\emph{Andrej started working on this, done by Monday}
{\oldText{Taken from XLite paper}
To investigate the empirical performance of our algorithm we will test it on a large-scale, real-world multilingual dataset that we extracted from Wikipedia  by  using so called 'inter-language' links as an alignment. We select a subset of Wikipedia languages containing three major languages, English--\emph{en} (hub language), Spanish--\emph{es}, Russian--\emph{ru}, and five minority (in the sense of Wikipedia sizes) languages, Slovenian--\emph{sl}, Piedmontese--\emph{pms}, Waray-Waray--\emph{war} (all with about 2 million native speakers), Creole--\emph{ht} (8 million native speakers), and Hindi--\emph{hi} (180 million native speakers). For preprocessing we remove the documents that contain less than 20 different words (stubs) and remove words occur in less than 50 documents as well as the top 100 most frequent words (in each language separately). We represent the documents as normalized TFIDF\cite{Salton88term-weightingapproaches} weighted vectors. These are languages with Wikipedia article sizes comparable to the minority languages.  (since the number of speakers does not directly correlate with the number of Wikipedia articles). The prime hub candidate is the English language which is well aligned with all other Wikipedia languages, although the alignment quality varies quite a bit. Furthermore, we remove the documents that contain less than 20 different words and remove words that are too infrequent as well as the top 100 most frequent words in the vocabularies. Furthermore, we call the document consisting of less than 20 different words, a stub. This documents are typically garbage, the titles of the columns in the table, remains of the parsing process, or Wikipedia articles with very little or no information contained in one or two sentences.

@@

In Section~\ref{sec:algorithms} we have described three main algorithms for identifying similar articles in different languages. These algorithms were $k$-means, LSI and CCA. To test which of these algorithms performs best we performed the following test. Using each algorithm, we analyzed all articles in Event Registry to find the most similar articles in other languages. The values of the cross-lingual article linking features (\texttt{linkCount} and \texttt{avgSimScore}) were then recomputed for all annotated learning examples. A dataset with only these two features and the label was constructed and used to test how accurate prediction models can be induced using the data. The results of the experiment are shown in Table~\ref{table:linkingEvalAlgos}. The table shows for each of the algorithms the obtained classification accuracy, precision and recall. We can see that the most informative features for cluster linking are obtained using the CCA algorithm, while $k$-means performs the worse. {\oldText{TODO:} add some explanation why this might be so.}
\emph{Andrej adds some tests, new experiment description graphs, and explanations for performance, done by Monday}
%15000 test documents, around 300 000 sth training documents
%Results for feature spaces of dimensions 500, 800, 1000  overfitting, 800 minor improvement
%Timex complexity of similarity computation scales linearly with dimension space. We double numbers of articles and decrease memory requirements by 1/2.
%CCA       CA          AUC         Prec        Recall
%CCA =     [0.7882      0.8504      0.7692	   0.8209
%           0.7957      0.8624      0.7788      0.8234
%           0.8031      0.8654      0.8015      0.8035];
%LSIS=     [0.7994      0.8627      0.7778      0.8358
%           0.7956      0.8634      0.7828      0.8159
%           0.7994      0.8642      0.8030      0.7910];
%LSIW=     [0.7894      0.8606      0.7673      0.8284;
%           0.7870      0.8632      0.7662      0.8234;
%           0.8018      0.8663      0.7854      0.8284];

%AMPR as function of the number of feature vectors
%500 is good, 800 better, 1000 overfitting, noise!
\includegraphics{slika.png}
%Why the hub approach?
%Optimize for language pairs in the system that have the largest number of articles in the system!
%Is star CCA really the best???
%Maybe omit this table?

@@

\subsection{Scaling}
\emph{Andrej asks who is the rest? I think that this section should be short.}
100 languages!
%Newsfeed volume
Describe the newsfeed volume, number of events and the number of similarities that need to be computed. Compare the memory requirements of our current implementation to the rest.
Comment on the caching gains in our implementation.
